### 2019-09-11 scache/tii/tex/abstract.tex
Fix typos
Revision for re-submit.

% In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. 
% {\color{black}
In industrial large-scale data-parallel analytics, shuffle, or the cross-network read and the aggregation of partitioned data between tasks with data dependencies, usually bring in large overhead.
Due to the dependency constraints, execution of those descendant tasks could be delayed by long shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
SCache adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
% By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{black}
We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze DAG frameworks and evaluate the SCache shuffle optimization. 
The FRQ model quantifies the utilization of resources and predicts the execution time of each phase of computing jobs. 
% We use the FRQ model to analyze DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
We have implemented SCache on both Spark and Hadoop MapReduce. The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop MapReduce, SCache optimizes end-to-end Terasort completion time by $15\%$.
}
\end{abstract}

>>>>

% In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. 
% {\color{black}
In industrial large-scale data-parallel analytics, shuffle, or the cross-network read and the aggregation of partitioned data between tasks with data dependencies, usually bring in large overhead.
% Due to the dependency constraints, execution of those descendant tasks could be delayed by long shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
SCache adopts heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
% By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{black}
We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze DAG frameworks and evaluate the SCache shuffle optimization. 
The FRQ model quantifies the utilization of resources and predicts the execution time of each phase of DAG jobs. 
% We use the FRQ model to analyze DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
We have implemented SCache on both Spark and Hadoop MapReduce. The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop MapReduce, SCache optimizes end-to-end Terasort completion time by $15\%$.
}
\end{abstract}

### 2019-09-11 scache/tii/tex/evaluation.tex
Fix typos
Revision for re-submit.

This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big-data analysis. 
% To show the compatibility of SCache as a cross-framework plug-in, we implement and evaluate SCache on both Spark and Hadoop MapReduce. 
We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big-data analysis.
% First, we evaluate the Spark with SCache in two different benchmarks.
% We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
% Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
% To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
% In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
% To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
% Second, due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
% Finally, we measure the overhead of weighted reservoir sampling. 
In summary, SCache decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
{\color{black}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.}

@@

\subsection{Setup}\label{stepup}
% We modified Spark to enable shuffle optimization of SCache as a representative.
The shuffle configuration of Spark is set to the default\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}. 
We run the experiments on a 50-node m4.xlarge cluster on Amazon EC2\footnote{http://aws.amazon.com/ec2/}. 
Each node has 16GB memory and 4 CPUs. The network bandwidth provided by Amazon is insufficient. 
Our evaluations reveal the bandwidth is only about 300 Mbps.
%  (see Figure \ref{fig:util}).

@@

To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
Although the simple DAG computing alleviates the effect of \textit{pre-scheduling}, the shuffle-heavy jobs can still be optimized by the SCache shuffle data management.

% Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. 
% As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase and the shuffle phase and the reduce phase start simultaneously. The beginning part of reduce phase needs to wait for network transfer because a large amount of shuffle data reaches the network bottleneck. This causes the CPU resources to be idle. 
On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase. This avoids the reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle I/O throughput in the map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after decoupling shuffle, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
}

@@

>>>>

@@

% This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big-data analysis. 
{\color{blue}
This section reveals a representative evaluation of SCache performance on both Spark and Hadoop MapReduce.
% To show the compatibility of SCache as a cross-framework plug-in, we implement and evaluate SCache on both Spark and Hadoop MapReduce. 
% We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big-data analysis.
In industrial big-data, SQL-based big-data technologies are widely used in these systems, such as data mining, predictive analytics, text analytics, and statistical analysis \cite{poess2017analysis}.
% SQL-Based Big Data Systems are widely used on industrial application.
% Because of the limited time and resource, 
To prove the performance gain of SCache in industry, 
we evaluate SCache with TPC-DS\footnote{http://www.tpc.org/tpcds/}.
TPC-DS is a standard benchmark which focus on modeling industrial workload.
% TPC-DS, TPCx-BB, HiBench, BigDataBenchmark, and so on are popular standard big data benchmarks which evaluate big data systems.
% TPC-DS models queries and data maintenance of a retail product supplier and provides a representative evaluation of performance.
% We believe using TPC-DS is able to evaluate the performance of SCache in industry. 
% First, we evaluate the Spark with SCache in two different benchmarks.
% We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
% Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
% To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
% In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
% To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
% Second, due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
% Finally, we measure the overhead of weighted reservoir sampling. 
% In summary, SCache decreases ~$89\%$ time of Spark shuffle without introducing extra network transfer.
% More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by SCache.
%  applying the optimization from SCache.
In summary, SCache decreases ~$89\%$ time of Spark shuffle and improves ~$40\%$ of the overall completion time of TPC-DS on average.
Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.
}

\subsection{Setup}\label{stepup}
% We modified Spark to enable shuffle optimization of SCache as a representative.
We use Spark version 1.6.2 and Hadoop MapReduce version 2.8.5.
The shuffle configuration of Spark is set to the default\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}. 
We run the experiments on a 50-node m4.xlarge cluster on Amazon EC2\footnote{http://aws.amazon.com/ec2/}. 
Each node has 16GB memory and 4 CPUs. The network bandwidth provided by Amazon is insufficient. 
Our evaluations reveal the bandwidth is only about 300 Mbps.
%  (see Figure \ref{fig:util}).

@@

{\color{blue}
% To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
% Although the simple DAG computing alleviates the effect of \textit{pre-scheduling}, the shuffle-heavy jobs can still be optimized by the SCache shuffle data management.
Unlike Spark, Hadoop MapReduce has only one Map and one Reduce phase.
Such a simple workflow alleviates the defect of the naive scheduling schemes and reduce the benefits of \textit{pre-scheduling}.
However, SCache can still provide considerable optimization on shuffle-heavy workloads.
We use Terasort benchmark to evaluate the performance gain of SCache and also prove the cross-framework ability of SCache.
% Although the simple workflow alleviates the benefits of \textit{pre-scheduling}, SCache can still .
% Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
% Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. 
% As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
}

As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase and the shuffle phase and the reduce phase start simultaneously. The beginning part of reduce phase needs to wait for network transfer because a large amount of shuffle data reaches the network bottleneck. This causes the CPU resources to be idle. 
On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase. This avoids the reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle I/O throughput in the map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after decoupling shuffle, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
}

@@

\subsection{The FRQ Model Evaluation}\label{model_evaluation}
% To evaluate the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster; (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
We run the Terasort as an experimental application on a Hadoop MapReduce framework.
% We deployed Hadoop with SCache and without SCache in both environments.

Table \ref{table1} shows the results of the FRQ model in the in-house environment.
% The workload is from 16 GB to 64 GB. 
\(D\) and \(N\) are set according to the application parameters. We calculate \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) according to the environment. We set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the reduce phase when enabling SCache. 
% The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are according to Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively. 
In the Hadoop with SCache, Terasort satisfies the situation in Figure \ref{fig:model_basic} (\(V_{Map} \times R \ge V_{Shuffle}\)). 
% thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}.
In the original Hadoop, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tmap}). \(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\). 
% The formula of \(Error\) is:
% \begin{equation}
% 	\label{equation_error}
% 	\begin{aligned}
% 		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
% 	\end{aligned}
% \end{equation}

Table \ref{table2} shows the results in Amazon EC2 environment.
% \;\(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices.
We set K to the same empirical value.
% The formulas in the table are all the same except \(T_{P\_Shuffle}\).
In this environment, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache2} (\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}. 
% In the previous case, \(T_{P\_Shuffle}\) is still equal to \(T_{Shuffle}\).

% \begin{figure}
% 	\centering
% 	\begin{subfigure}{0.49\linewidth}
% 		\includegraphics[width=\linewidth]{fig/hadoop_net1}
% 		\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
% 		\label{fig:hadoop_net1}
% 	\end{subfigure}
% 	\begin{subfigure}{0.49\linewidth}
% 		\includegraphics[width=\linewidth]{fig/hadoop_net2}
% 		\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
% 		\label{fig:hadoop_net2}
% 	\end{subfigure}
% 	\caption{\color{black}Network utilization on Hadoop MapReduce with SCache}
% 	\label{fig:hadoop_net}
% \end{figure}

% In order to evaluate the two cases as mentioned above when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}. Figure \ref{fig:hadoop_net1} shows that, in the in-house environment, the network utilization remains high until the shuffle phase is completed. On the other hand, Figure \ref{fig:hadoop_net2} shows that the network utilization has 5 regular peaks in Amazon EC2 environment. 
% Both these two situations are consistent with the FRQ model in Figure \ref{fig:model_scache}. 
% Therefore, we believe that the FRQ model is able to accurately describe the performance of a framework with SCache.

Regarding accuracy, the experimental values are all larger than the calculated values. This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, etc. 
% In the case where the input data is small and the total time is short, the error caused by the overhead is amplified. 
This overhead will be amplified when the input data is small or the total execution time is short. 
Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is mainly below 10\%, such errors are acceptable. Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
}

\begin{table*}
\centering
\scalebox{0.95}{
	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
	\hline
	&
	\(D\) &	
	\(R\) &	
	\(N\) &	
	\(V_{Map}\) &	
	\(V_{Reduce}\) &	
	\(V_{Shuffle}\) &	
	\(K\) &	
	\(T_{Map}\) &	
	\(T_{Shuffle}\) &	
	\(T_{P\_Shuffle}\) &
	\(T_{Reduce}\) & 
	\(T_{Job}\) & 
	\(Exp T_{Job}\) &
	\(Error\)\\

	\hline
	& 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
	SCache
	& 32	& 1	& 4 &	0.65 &	1 &	0.47 &	0.5 &	49.23 &		68.09	 &	31.16 &	47.58 &	96.81	& 104 & 	6.91\% \\
	& 48	& 1	& 6 &	0.65 &	1 &	0.47 &	0.5 &	73.85 &		102.13 &	40.59 &	68.29 &	142.14	& 151 & 	5.87\% \\
	& 64	& 1	& 8 &	0.65 &	1 &	0.47 &	0.5 &	98.46 &		136.17 &	50.02 &	89.01 &	187.47	& 193 & 	2.87\% \\
	\hline
	& 16	& 1 & 2 &	0.65 &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
	Legacy
	& 32	& 1 & 4 &	0.65 &	1 &	0.47 &	0.6 &	49.23 &		68.09	&	68.09	&	72.85	&	122.08	&	135	&	9.57\%	\\
	& 48	& 1 & 6 &	0.65 &	1 &	0.47 &	0.6 &	73.85 &		102.13	&	102.13	&	109.28	&	183.12	&	188	&	2.59\%	\\
	& 64	& 1 & 8 &	0.65 &	1 &	0.47 &	0.6 &	98.46 &		136.17	&	136.17	&	145.70	&	244.16	&	249	&	1.94\%	\\
	\hline
	\end{tabular}
}
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\caption{\color{black}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
\label{table1}
\end{table*}
% \subsection{Performance Analysis}\label{model_performance_analysis}

% \begin{table*}[!t]
\begin{table*}
\centering
\scalebox{0.95}{
	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
	\hline
	&
	\(D\) &	
	\(R\) &	
	\(N\) &	
	\(V_{Map}\) &	
	\(V_{Reduce}\) &	
	\(V_{Shuffle}\) &	
	\(K\) &	
	\(T_{Map}\) &	
	\(T_{Shuffle}\) &	
	\(T_{P\_Shuffle}\) &
	\(T_{Reduce}\) & 
	\(T_{Job}\) & 
	\(Exp T_{Job}\) &
	\(Error\)\\

	\hline
	& 128	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	111.30 &	91.43	&	18.29	&	96.81	&	208.12	&	232	&	10.29\%	\\
	SCache
	& 256	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	222.61 &	182.86	&	36.57	&	193.63	&	416.24	&	432	&	3.65\%	\\
	& 384	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	333.91 &	274.29	&	54.86	&	290.44	&	624.36	&	685 &	8.85\%	\\
	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	445.22 &	365.71	&	91.43	&			&	841.62	&	1135 &	25.85\%	\\
	\hline
	& 128	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	111.30 &	91.43	&	91.43	&	142.53	&	253.83	&	266 &	4.57\%	\\
	Legacy
	& 256	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	222.61 &	182.86	&	182.86	&	285.06	&	507.67	&	524 &	3.12\%	\\
	& 384	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	333.91 &	274.29	&	274.29	&	427.59	&	761.50	&	776 &	1.87\%	\\
	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	445.22 &	365.71	&	365.71	&	588.40	&	1033.62	&	1312 &	21.22\%	\\

	\hline
	\end{tabular}
}
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\caption{\color{black}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
\label{table2}
\end{table*}

### 2019-09-11 scache/tii/tex/impl.tex
Revision for re-submit.

\section{Implementation}\label{impl}
This section presents an overview of the implementation of SCache. 
{\color{black}
We first present the system overview and the detail of sampling in Subsection \ref{arch}. 
The following \ref{memorymanage} subsection focuses on two constraints on memory management.
% In Subsection \ref{crossframework}, we evaluate the cross-framework capability of SCache. 
% At last, we discuss the cost of adapting SCache and fault tolerance. 
}

\subsection{System Overview}\label{arch}
SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a worker daemon. As a plug-in system, SCache needs to rely on a DAG framework.
As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture for the shuffle data management system. 
The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
% The coordination provides two guarantees: (a) data is stored in memory before tasks start and (b) data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
The daemon bridges the communication between DAG framework and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to the original scheduler in framework.
When a DAG job is submitted, the DAG information is generated in framework task scheduler. 
Before the computing tasks begin, the shuffle dependencies are determined based on DAG.
For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included. If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling job before the computing job.
The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition.
The result will be aggregated on SCache master to predict the reduce partition size.
% We will elaborate the sampling procedure in the Section \ref{sampling}.

{\color{black}
When a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API to move all the blocks out of framework worker through memory copy and release the slot immediately.
% After that, the slot will be released (without being blocked on disk operations).
When a block of the map output is received, the SCache worker will send the block ID and the size to the master.
If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
To enforce the DAG framework to run according to the SCache pre-scheduled results, we also insert some lines of codes in framework scheduler.
% After modification, the DAG scheduler consults SCache co-scheduler to get the preferred location for each task.
}

@@

\subsection{Memory Management}\label{memorymanage}
% As mentioned in Section \ref{observation}, though the shuffle size is relatively small, memory management should still be cautious enough to limit the effect of performance of DAG framework.
When the size of cached blocks reaches the limit of reserved memory, SCache flushes some of them to the disk temporarily, and re-fetches them when some cached shuffle blocks are consumed or pre-fetched. 
To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data --- \textit{all-or-nothing} and \textit{context-aware-priority}.

\subsubsection{All-or-Nothing Constraint}
% This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
{\color{black}
% Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
Both experience and DAG framework manuals (e.g., Hadoop and Spark) recommend that multi-round execution of each stage will benefit the performance of applications.
If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
% PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
% Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least.
Therefore, SCache master sets blocks of one round as the minimum unit of storage management.
We refer to this as the all-or-nothing constraint.
% According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets blocks of one round as the minimum unit of storage management.
}
% For those incomplete units, SCache marks them as the lowest priority.

@@

% \subsection{Discussion of Fault Tolerance}\label{fault}
% Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present. 
% We plan to implement SCache master with Apache ZooKeeper \footnote{https://zookeeper.apache.org/} to provide constantly service. 
% If a failure happens inside the SCache worker, SCache daemon can block the shuffle write/read operations until the worker process restarts without violating the correctness of the DAG computing.
% A possible way to handle this failure is selecting some backup nodes to store replications. 
% % But the replications can introduce a significant network overhead \cite{availability}.  
% Currently, we leave the sever faults (e.g., the failure of a node) to the DAG frameworks. 
% We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 
% Meanwhile, SCache can still provide shuffle optimization during the recovery.

>>>>

\section{Implementation}\label{impl}
This section presents an overview of the implementation of SCache. 
We first present the system overview and the detail of sampling in Subsection \ref{arch}. 
The following \ref{memorymanage} subsection focuses on two constraints on memory management.
% In Subsection \ref{crossframework}, we evaluate the cross-framework capability of SCache. 
% At last, we discuss the cost of adapting SCache and fault tolerance. 
{\color{blue}
In Subsection \ref{fault}, we discuss the fault tolerance of the system.
}

\subsection{System Overview}\label{arch}
{\color{blue}
As shown in Figure \ref{fig:architecture}, SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a worker daemon.
As a plug-in system, SCache needs to rely on a DAG framework. 
The master node of SCache includes a DAG co-scheduler and a storage manager.
The DAG co-scheduler is responsible for pre-scheduling the reduce tasks assignment and then forcing the DAG framework to assign reduce tasks according to this assignment.
The storage manager is used for managing the shuffle blocks saved in worker nodes.
% The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
% The coordination provides two guarantees: (a) data is stored in memory before tasks start and (b) data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
% The daemon bridges the communication between DAG framework and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to the original scheduler in framework.

When a DAG job is submitted, the DAG information is generated in the framework task scheduler. 
% Before the computing tasks begin, the shuffle dependencies are determined based on DAG.
% For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.
If the RangePartitioner or a customized non-hash partitioner is used, SCache will insert an extra sampling job before the job starts.
The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition to gather the sample data.
SCache master predicts the reduce partition size based on the data and then call Algorithm \ref{hminheap} or \ref{mhminheap} to do the pre-scheduling.

% After a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API to move all the blocks out of framework worker through memory copy and release the slot immediately.
After a map task finishes computing, the shuffle writes in the map task is modified to use SCache API to memory copy all shuffle blocks to the SCache worker reserved memory.
% After that, the slot will be released (without being blocked on disk operations).
The SCahce records the block ID and the size and sends them to the master.
% When a block of the map output is received, the SCache worker will send the block ID and the size to the master.
% If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
If the collected shuffle blocks reach a threshold, the SCache co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks.
After pre-scheduling, SCahce workers start pre-fetching shuffle blocks according to the assignment from the master.
To enforce the DAG framework to assign tasks according to the SCache pre-scheduled results, we also insert some lines of codes in the framework scheduler.
}
% After modification, the DAG scheduler consults SCache co-scheduler to get the preferred location for each task.

@@

\subsection{Memory Management}\label{memorymanage}
% As mentioned in Section \ref{observation}, though the shuffle size is relatively small, memory management should still be cautious enough to limit the effect of performance of DAG framework.
{\color{blue}
SCache uses bellowed memory management to ensure performance.
If the reserved memory is running out, SCache will flush some of the blocks into the disk temporarily and then re-fetch them if needed.
SCache leverages two constraints to manage the shuffle blocks: \textit{all-or-nothing} and \textit{context-aware-priority}.
% When the size of cached blocks reaches the limit of reserved memory, SCache flushes some of them to the disk temporarily, and re-fetches them when some cached shuffle blocks are consumed or pre-fetched. 
% To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data --- \textit{all-or-nothing} and \textit{context-aware-priority}.
}

\subsubsection{All-or-Nothing Constraint}
% This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
{\color{blue}
% Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
% Both experience and DAG framework manuals (e.g., Hadoop and Spark) recommend that multi-round execution of each stage will benefit the performance of applications.
As discussed in the observation in Subsection \ref{observation}, it is common to have multi-round execution of each stage. 
If one of the task in a round missed a memory cache, the re-fetch overhead will become a bottleneck and then slow down the whole stage. 
% If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
% PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
% Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least.
}
Therefore, SCache master sets blocks of one round as the minimum unit of storage management.
We refer to this as the all-or-nothing constraint.
% According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets blocks of one round as the minimum unit of storage management.
% For those incomplete units, SCache marks them as the lowest priority.

@@

{\color{blue}
\subsection{Discussion of Fault Tolerance}\label{fault}
% how to handle faults? -> maybe replication -> tradeoff
For now, SCache only restarts failed workers without recovering their data.
SCache leaves the fault handling to the DAG frameworks.
If a failure happens in a SCache worker during shuffle phases, the $getBlock$ API will return a data not found error which causes the DAG framework restarts the current stage.
During the re-computing, the DAG frameworks still use SCache to gain shuffle optimization.
A possible way to avoid this re-computing is to use replications to recover the data.
However, such replications can introduce a significant network overhead.
We believe that the current way is more promising because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as the paralleled recovery of Spark. 
% Meanwhile, SCache can still provide shuffle optimization during the re-computing.
}

% Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present.
% We plan to implement SCache master with Apache ZooKeeper \footnote{https://zookeeper.apache.org/} to provide constantly service. 
% If a failure happens inside the SCache worker, SCache daemon can block the shuffle write/read operations until the worker process restarts without violating the correctness of the DAG computing.
% A possible way to handle this failure is selecting some backup nodes to store replications. 
% % But the replications can introduce a significant network overhead \cite{availability}.  
% Currently, we leave the sever faults (e.g., the failure of a node) to the DAG frameworks. 
% We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 
% Meanwhile, SCache can still provide shuffle optimization during the recovery.
